%-------------------------
\documentclass[legalpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{tfrupee} 
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[letterpaper,margin=1in]{geometry}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeListItem}[1]{
  \vspace{-1pt}\item\small{
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    #1
    \end{tabular*}\vspace{-5pt}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\footskip}{4.08003pt}
\begin{document}
%\setstretch{1.15}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.cybertechtok.com}{\Large Arka Mukherjee}} & Email : \href{mailto:arka.mukherjee078@gmail.com}{\textcolor{blue}{arka.mukherjee078@gmail.com}}\\
  \textcolor{blue}{\href{http://cybertechtok.com/}{[Website]}} \textcolor{blue}{\href{https://github.com/ArkaMukherjee0}{[GitHub]}} & Mobile : +91-97490-60670 \\
\end{tabular*}


\resumeSubHeadingListStart
  \resumeSubItem{Research Focus}{LLM reasoning, multimodality, and AI agents with a human-computer and agent-computer interaction focus}
\resumeSubHeadingListEnd
%\vspace{0.1cm}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kalinga Institute of Industrial Technology (KIIT)}{Bhubaneswar, India}
      {Bachelor of Technology in Computer Science;  Cumulative GPA: 9.73/10.0}{July 2023 - May 2027 (Expected)}
      \resumeItemListStart
        \resumeSubItem{Relevant Courses}
        {Agentic AI, Probability \& Statistics, Data Analytics, Machine Learning, AI, Algorithms, Data Mining, Human-Computer Interaction (Coursera)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University - Dr. Min Xu}{Remote}
      {Research Intern}{January - May 2026}
      \resumeItemListStart
        \resumeItem{Reinforcement Learning}
            {Applied GRPO, DPO, and PPO to study RL generalization to low-sampling decoding tasks (64-token action space). Improved VRAM efficiency and iterated GRPO on 800k+ datapoints.}{}
    \resumeItemListEnd
    \resumeSubheading
      {IIT Bhubaneswar - Dr. Shreya Ghosh}{Bhubaneswar, India}
      {Undergraduate Research Fellow (Funded)}{December 2024 - Present}
      \resumeItemListStart
        \resumeItem{Multimodal STEM reasoning}
            {Developed mmJEE-Eval, a multimodal reasoning benchmark of 1,460 STEM problems to combat saturation (Qwen 3 VL 235B scored 45\% vs 85\% on Math Vista). Evaluated 17 VLMs and discovered metacognitive barriers: VLMs detect 53\% of errors but correct only 3.5\%.} \textit{(IJCNLP-AACL 2025)}% \textit{(Submitted to ARR October 2025)}
        \resumeItem{Multimodal Cultural Competence}
            {Created the first systematic \textbf{evaluation framework for VLM cultural competence} via story generation on 5 VLMs with a novel evaluation metric. \textit{(Oral @ ICCV 2025 ASI workshop)}}
        \resumeItem{Integrated Capability Evaluation (ICE)}
            {Proposed \textbf{ICE}, a new evaluation paradigm unlike benchmarks and leaderboards that models real-world tasks. Tested 5 frontier models across 7 scaffolds on a tiered diagnostic setup, showing GPT-5.2 Codex, Claude Sonnet 4.6 collapse universally.}
        \resumeItemListEnd

    \resumeSubheading
     {IIT Ropar - Dr. Sudarshan Iyengar}{Ropar, India}
     {Summer Research Fellow (IASc-INSA-NASI)}{May 2025 - July 2025}
     \resumeItemListStart
       \resumeItem{VLM Benchmarks}
           {Developed \textbf{EduVLM-Bench} for STEM prerequisite detection and evaluated OSS LLMs. The top model, Gemma3 27B, achieved 38.5\% accuracy.}% }
     \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS------------
\section{Publications}
    \begin{enumerate}[itemsep=0pt]
    \small
        \item Mukherjee, A., \& Ghosh, S. (2025). \href{https://openaccess.thecvf.com/content/ICCV2025W/ASI/papers/Mukherjee_Toward_Socially_Aware_Vision-Language_Models_Evaluating_Cultural_Competence_Through_Multimodal_ICCVW_2025_paper.pdf}{\textcolor{blue}{Toward Socially Aware Vision-Language Models: Evaluating Cultural Competence Through Multimodal Story Generation} (ICCV 2025 ASI workshop - Oral)}

        \item Mukherjee, A., \& Ghosh, S. (2025). 
        \href{https://arxiv.org/abs/2511.09339}{\textcolor{blue}{mmJEE-Eval: A Bilingual Multimodal Benchmark for Evaluating Scientific Reasoning in Vision-Language Models} (IJCNLP-AACL 2025 Findings, 12\% acceptance rate)}

    \end{enumerate}


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://huggingface.co/datasets/ArkaMukherjee/reasoning-10k-v2}{Automated VLM reasoning dataset generator}}
      {Curated 10k samples for SFTing VLMs. Our method achieved the best VMCBench results, beating Walton Cold Start and MM MathInstruct. \textit{(Ranked \#6 in NeurIPS DCVLR challenge)}}% (the model had no prior knowledge of iPhone 16).}
  \resumeSubHeadingListEnd

%--------ACHIEVEMENTS/EXTRACURRICULARS------------
\section{Achievements/Extracurriculars}
\resumeSubHeadingListStart
    % \resumeSubItem{IASc-INSA-NASI Summer Research Fellowship (2025)}{}
    \resumeSubItem{Awards}{\textbf{KIIT Merit Scholar} (Dean's list) for 5 semesters, \textbf{IUSSTF-Viterbi Scholar} at the University of Southern California (one of 15 students selected from India), \textbf{Amgen Scholars} Summer Research Program (declined), \textbf{Aalto Science Institute (AScI)} Summer Research Program in Finland (declined)}
    \resumeSubItem{Outreach}{Published articles (10M+ reads) and hardware reviews in collaboration with Nvidia, AMD, and ASUS.} %\textcolor{blue}{\href{https://www.sportskeeda.com/author/thegamingfire2020-rpw6l}{[Sportskeeda]}}}

    \resumeSubItem{Nvidia GPU Sponsorship}{Received RTX 5090, 5080, and 5070 GPUs from Nvidia India for AI research.} 
    \resumeSubItem{Travel Awards \& Grants}{D\&I Subsidy award at IJCNLP-AACL'25 (\$750), AI Grants India (API keys and credits)}

%--------PROGRAMMING SKILLS------------
\section{Technologies and Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
    {Python (advanced), Java, C, SQL}
     
    \resumeSubItem{ML/NLP Frameworks}
     {PyTorch, HF Transformers, Datasets \& TRL, Unsloth, LM Studio, Docker, Agentic AI (Langchain, Playwright, mini-SWE-agent)}
   
 \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
